A VCG-Based Mechanism for Electronic Commerce Applications

### 2019-09-13 ec-18/sample-ec-submission.tex

	The work is supported by the \grantsponsor{GS501100001809}{National
		Natural Science Foundation of
		China}{http://dx.doi.org/10.13039/501100001809} under Grant
	No.:~\grantnum{GS501100001809}{61273304\_a}
	and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
		Scientsts' Support Program}.

>>>>

	The work is supported by the \grantsponsor{GS501100001809}{National
		Natural Science Foundation of
		China}{https://doi.org/10.13039/501100001809} under Grant
	No.:~\grantnum{GS501100001809}{61273304\_a}
	and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
		Scientsts' Support Program}.
